An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
missing entry

\item \app employs a collection of machine learning algorithms to 
enable powerful rule and constraint inference without assistance 
from any pre-defined templates.

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors.

>>>>

\item \app employs a collection of machine learning algorithms to 
enable powerful rule and constraint inference.

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
missing entry errors, and environment-related errors.

### 2016-05-10 OSDI/learner.tex
missing entry

With a configuration file that has been verified against catastrophic
failures (\eg, entry missing, type, and ordering errors), 
the user may also want to examine more subtle issues.
Anomalous values can cause tricky, but impactful, performance and memory
issues that are hard to debug, as discussed in Example 4 of 
$\S$\ref{sec-motiv}. 
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.

>>>>

With a configuration file that has been verified against catastrophic
failures (\eg, missing entry, type, and ordering errors), 
the user may also want to examine more subtle issues.
Anomalous values can cause tricky, but impactful, performance and memory
issues that are hard to debug, as discussed in Example 4 of 
$\S$\ref{sec-motiv}. 
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.

### 2016-05-10 OSDI/motiv.tex
missing entry

\para{Example~3: Missing entry error.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem a {\em missing entry error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry errors.
Below is a real-world entry missing error example~\cite{yin11anempirical}:
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
achieved via the following entries in the OpenLDAP configuration file:

>>>>

\para{Example~3: Missing entry error.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem a {\em missing entry error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry errors.
Below is a real-world missing entry error example~\cite{yin11anempirical}:
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
achieved via the following entries in the OpenLDAP configuration file:
